Assertion Contracts

### 2024-08-01 papers/assertion-contract/assertion_contract_app/paper.tex
Experiments

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{graphicx}
%\usepackage{fixme}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{titling}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{comment}

@@

%For example, given \( n = 10000 \) and \( p = 0.8 \), the number of seeds \( m \) needed to achieve the desired probability is calculated as follows:
%\[
%m = \frac{\ln(1 - 0.8)}{\ln\left(1 - \frac{1}{10000}\right)}
%\]

%\[
%m = \frac{\ln(0.2)}{\ln\left(1 - 0.0001\right)}
%\]

%\[
%m = \frac{-1.6094}{\ln(0.9999)}
%\]

%\[
%m = \frac{-1.6094}{-0.0001}
%\]

%\[
%m \approx 16094
%\]

%Therefore, approximately \( 16094 \) seeds are needed to have an \( 80\% \) chance of finding a counterexample.

@@

Figure \ref{fig:gas_compare} shows the gas consumption for both methods. The red line shows the gas consumed by the on-chain verification method, which increases linearly with the size of the parameter. The blue line shows the gas cost by the offline distributed method. We can see that in the beginning, when the size of the parameter is small, it costs more with the offline method than with the on-chain method, but at one point it will show its benefits.

@@

Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks. However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
\section{Domain Specification Language for Assertion}
\note{To discuss: if it make sense to design}
\section{Converter - Generating an Assertion Contracts} 
\note{To discuss: if it make sense to implement}
\section{Prototype Implementations}
\note{TODO}
\subsection{Sorted array}
%There are two possible data structures for storing such records: map and array. For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
%\begin{lstlisting}[numbers=none]
%   struct Parameter {
%        bytes32 p_hash;
%        uint256 timestamp;
%    }
% mapping (address => Parameter) public parameters;
%\end{lstlisting}

>>>>

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{graphicx}
%\usepackage{fixme}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{titling}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{comment}
\usepackage{array}
\usepackage{booktabs}

@@

@@

Figure \ref{fig:gas_compare} shows the gas consumption for both methods assuming that $G_{base}$ remains unchanged regardless of the parameter size. The red line shows the gas consumed by the on-chain verification method, which increases linearly with the size of the parameter. The blue line shows the gas cost by the offline distributed method. We can see that in the beginning, when the size of the parameter is small, it costs more with the offline method than with the on-chain method, but at one point it will show its benefits.

@@

Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks. However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
\section{Domain Specification Language for Assertion}
\note{To discuss: if it make sense to design}
\section{Converter - Generating an Assertion Contracts} 
\note{To discuss: if it make sense to implement}
\section{Prototype Implementations}
\subsection{Decentralize Selling Flatform}
\subsubsection{On-chain verification}
\subsubsection{Off-chain distributed verification}
\subsubsection{Gas comperation}
\begin{table}[h]
\centering
\caption{Gas Consumption Comparison}
\begin{tabular}{c|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3cm}|c}
\toprule
Parameter Size & Line 1 Gas Consumption & Line 2 Gas Consumption & Difference \\
\midrule
05  &  504225   &  578196   &  -73971   \\
10  &  903555   &  908838   &  -5283   \\
20  &  1842037  &  1804283  &  37754  \\
30  &  2797283  &  2733927  &  63356  \\
50  &  4708543  &  4593215  &  115328 \\
70  &  6714839  &  6545213  &  169626 \\
100 &  9581470  &  9333977  &  247493 \\
120 &  11492538 &  11193157 &  299381 \\
150 &  14359469 &  13981933 &  377536 \\
170 &  16270716 &  15841101 &  429615 \\
200 &  19137934 &  18629877 &  508057 \\
\bottomrule
\end{tabular}
\end{table}

\begin{tikzpicture}
\begin{axis}[
    title={Gas Consumption Comparison},
    xlabel={Parameter Size},
    ylabel={Gas Consumption},
    legend pos=north west,
    grid=major,
    width=10cm,
    height=6cm
]

% Line 1 data
\addplot[
    color=blue,
    mark=*,
    ]
    coordinates {
    (5, 504225) (10, 903555) (20, 1842037) (30, 2797283) (50, 4708543) (70, 6714839) (100, 9581470) (120, 11492538) (150, 14359469) (170, 16270716) (200, 19137934)
    };
    \addlegendentry{Centralize}

% Line 2 data
\addplot[
    color=red,
    mark=square*,
    ]
    coordinates {
    (5, 578196) (10, 908838) (20, 1804283) (30, 2733927) (50, 4593215) (70, 6545213) (100, 9333977) (120, 11193157) (150, 13981933) (170, 15841101) (200, 18629877)
    };
    \addlegendentry{Decentralize}

\end{axis}
\end{tikzpicture}

\begin{tikzpicture}
\begin{axis}[
    title={Difference in Gas Consumption},
    xlabel={Parameter Size},
    ylabel={Difference in Gas Consumption},
    legend pos=north west,
    grid=major,
    width=10cm,
    height=6cm
]

% Difference data
\addplot[
    color=green,
    mark=square*,
    ]
    coordinates {
    (5, -73971) (10, -5283) (20, 37754) (30, 63356) (50, 115328) (70, 169626) (100, 247493) (120, 299381) (150, 377536) (170, 429615) (200, 508057)
    };
    \addlegendentry{Difference}

\end{axis}
\end{tikzpicture}

\subsection{Sorted array}
%There are two possible data structures for storing such records: map and array. For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
%\begin{lstlisting}[numbers=none]
%   struct Parameter {
%        bytes32 p_hash;
%        uint256 timestamp;
%    }
% mapping (address => Parameter) public parameters;
%\end{lstlisting}
